The parabolic equation arises in the modelings of a number of phenomenas such as heat transfer and financial process. In which, the solving of boundary value problem act as major role.\\
In the aspect of thermal engineering, parabolic partial differential equation or heat equation is used to describe time dependent heat transfer process via conduction in solid objects. Its solution is the thermal distribution or variation in temperature inside the being observed domain. Wide range in such field of engineering require the simulation of heat transfer and numerically solving of heat equation.\\
Freefem++ provides efficient tools in solving and modeling PDE systems, where parabolic equation is one of the most basics. Although it has build in visualize tool, extend module medit provides powerful visualization features. Our work focus on the application of Freefem++ in various problems of the heat equation.\\
First we approach the common boundary value problem. As it is the most basic problem of parabolic equation, numerous researches have been done. Although Freefem++ does not have build-in-solver for such case, time discrete schemes could be applied. The detail method and Freefem++ implementation are discussed.\\
Various numerical experiments have been done to show Freefem++ ability in finite element analysis. We studied the error convergence with exact solution in a specific case. Also, a shape optimization problem arises in thermal engineering was briefly mentioned. Lastly, an optimal control problem of parabolic equation was performed using module IPOPT.
