% 6 pages max
\documentclass[twocolumn]{article}
\input{packages_and_definitions} 

\title{\bf Numerical simulation of heat transfer problem by Freefem++ software}
\author{Ta Thi Thanh Mai\thanks{email: mai.tathithanh@hust.edu.vn}\and Ho Duc Nhan\thanks{email: hdnhan28@gmail.com}\and Tran Minh Tam\thanks{email: tam.tranminh22@gmail.com}}
%\thanksmarkseries{arabic}
\date{\footnotesize\textit{School of Applied Mathematics and Informatics, Hanoi University of Science and Technology, No.1 Dai Co Viet street, Hai Ba Trung District, Hanoi, Vietnam}}
\justifying
% ---------------------------------------------
\begin{document}
\twocolumn[
	\maketitle
	\begin{@twocolumnfalse}
		\rule{\textwidth}{.1pt}
		\begin{abstract}
		We study the problem of heat transfer and its application in engineering. The main purpose of this paper is to present a numerical scheme for parabolic equations in FreeFem++ and implement some simulations of heat equation in shape design and optimal control problem. We propose a variational method in combination with continuous Galerkin finite element methods and an implicit scheme for discretization in time. A numerical scheme with error estimate are given for direct problem. The optimal control problem is solved by using IPOPT optimizer. Some numerical examples are investigated for showing the efficiency and accuracy of present solver.
		\end{abstract}
		\vspace{1ex}
		\noindent \textit{Keywords: Crank-Nicolson, parabolic equations, backward Euleur, Galerkin finite element, optimal control.
		}
		\\
		\rule{\textwidth}{.1pt}
		\vspace{2mm}
	\end{@twocolumnfalse}
]
\saythanks

% --------------------------------------------------------------------
\section{Introduction}
\quad Heat transfer via conduction in solid objects is an important part in thermal engineering and solid mechanics. Its mathematical expression, the parabolic equation has received a large amount of attention from engineers and mathematicians. Despite a vast literature on numerical solving of this problem, it still requires further investigation to reach challenging modelings. 

In this article, we aim to construct a numerical scheme for parabolic equation and apply it to simulate one case of thermal engineering and optimal control problems. We focus on numerical simulations by using Freefem++ \url{https://freefem.org}, an efficient tool for solving PDE equations and visualization software medit \cite{Fre01}. The main contribution of this work is giving a solver of heat equation with exhaustive study for error convergence. This is an important feature to simulate more complex modeling in thermal engineering and other problem.

This paper is organized into five sections. The next section 
describes our approach of heat equation by a common boundary value problem. Section 3 presents the numerical method: a variational formulation with an implicit scheme for time discretization and finite element methods for space discretization. All the numerical test cases are outlined in Section 4.  The last section gives some perspectives and comments about the effectiveness and reliability of the present scheme.
\section{Setting of problem}
% --------------------------------------------------------------------
\quad Let $\Omega \subset \mathbb{R}^d,\, d\in \mathbb{N^+}$ be a bounded domain with a boundary $\Gamma$ and denote the cylinder $Q=\Omega\times (0,\, T]$ and the lateral surface area $S=\Gamma \times [0,\, T]$ where $T>0$. 

Consider the heat equation:
\begin{align}\label{1.1}
	\frac{\partial u(x, t)}{\partial t}+\mathcal{L}u(x, t)=F(x, t), \quad(x, t)\in Q,
\end{align}
with the Dirichlet boundary and initial conditions, respectively
\begin{align}
	u(x, t)&=0,\quad(x, t)\in S, \label{1.2}\\
	u(x, 0)&=u_0(x),\quad\quad\, x\in \Omega,\label{1.3}
\end{align}
where
\begin{align*}
	&\mathcal{L}u = -\sum_{i, j=1}^{d}\frac{\partial}{\partial x_i}\left(a_{ji}\frac{\partial u}{\partial x_j}\right)+a_0u,\\
	&a_{ji}\in L^{\infty}(Q),\, a_{ij}=a_{ji},\; \forall i, j\in \{1, 2, ..., d\},\\
	&\lambda_1\left\|\xi\right\|^2\leq \sum_{i, j=1}^{d}a_{ij}\xi_i\xi_j\leq \lambda_2\left\|\xi\right\|^2,\; \forall \xi\in\mathbb{R}^d,\\
	&a_0\in L^{\infty}(Q),\; 0\leq a_0(x, t)\leq \mu_1,\; (x, t)\in Q,\\ 
	&u_0\in L^2(\Omega),%\;u_D\in L^2(S),
\end{align*}
with $\lambda_1$ and $\lambda_2$ are positive constants and $\mu_1\geq 0$. 

The problem is that to determine $u(x, t)$ when all data $a_{ji}(x, t),\,a_0(x, t),\,u_0(x)$ and $F(x, t)$ in equations \eqref{1.1} - \eqref{1.2} - \eqref{1.3} are given called direct problem.
% --------------------------------------------------------------------
\section{Numerical method} 
% --------------------------------------------------------------------
\subsection{Variational problem}
% --------------------------------------------------------------------
\quad Multiplying \eqref{1.1} by an efficient smooth test function $v$, integrating over $\Omega$ and then applying Green's formula, see \cite{F05}, leads to the problem: Find $u(.,t)\in H^1_0(\Omega)$ such that
\begin{align}\label{2.1}
	\left\langle \frac{\partial u}{\partial t}, v \right\rangle+a\left(u, v\right)=\left\langle F, v \right\rangle,\; \forall v\in H^1_0(\Omega),
\end{align} 
\begin{align}\label{2.2}
	u(x, 0)=u_0(x), \; x\in \Omega,
\end{align}
where 
$$a\left(u, v\right)=\int_{\Omega}\left[\sum_{i, j=1}^{d}a_{ji}\frac{\partial u}{\partial x_i}\frac{\partial v}{\partial x_j}+a_0uv\right]dx,$$
$$\left\langle F, v \right\rangle=\int_{\Omega}F vdx.$$

Following \cite{L98, W87, C87, SV03}, we can prove that there exists a unique solution of the problem \eqref{2.1} - \eqref{2.2}. We approximate this solution by finite element method as follows. 
\subsection{Finite element method}
\quad Now we present a fully discrete finite element approximation for the variational problem \eqref{2.1}.
\begin{itemize}
	\item For \textit{spatial approximation}, let $\mathcal{T}_h$ be a triangulation of $\Omega$ and define a piecewise linear finite element space $V_h \subset H^1_0(\Omega)$ by
	$$V_h=\left\{v_h:v_h\in C(\overline{\Omega}), v_h|_K\in P_1(K), \forall K\in \mathcal{T}_h\right\},$$
	where $P_1(K)$ is a continuous piecewise linear polynomial on the element $K$.
	\item For \textit{time discretization}, discrete $[0, T]$ uniformly into $M$ steps, where $t_n=n\Delta t,\, n=0, 1, \dots, M$ with the time step size $\Delta t = T/M$. Denote a function $u(x, t_n)=u^n(x)$.
\end{itemize}

Therefore, the problem is to find $u^n_h\in V_h$ for $n=1, 2, \dots, M$ with $\theta \in [0, 1]$ such that
\begin{align}\label{2.3}
	&\langle d_tu^n_h, v_h \rangle+a\left(\theta u^n_h+(1-\theta)u^{n-1}_h, v_h\right)\notag\\
	&\qquad\quad=\left\langle \theta F^n+(1-\theta)F^{n-1}, v_h \right\rangle, \; \forall v_h\in V_h,
\end{align}
and the initial condition 
\begin{align}\label{2.4}
	u^0_h=u_0,
\end{align}
where $d_tu^n_h=\frac{u^n_h-u^{n-1}_h}{\Delta t}, \; n=1, 2, ..., M$.

We have different methods depending on $\theta$ such as backward Euler ($\theta=1$) and Crank-Nicolson ($\theta=0.5$). The discrete variational problem \eqref{2.3} -\eqref{2.4} admits a unique solution $u^n_h\in V_h$. Let $u_h(x, t)$ be the linear interpolation of $u_h^n$ with respect to $t$. Therefore, for $x\in \Omega,\, t\in [t_{n-1}, t_n]$, we have
\begin{align*}
	u_h(x, t)=\frac{t-t_{n-1}}{\Delta t}u_h^{n-1}+\frac{t_n-t}{\Delta t}u_h^{n}.
\end{align*}
\begin{dl}\label{dl2.1}
	Let $u(x, t)$ be the solution of variational problem \eqref{2.1} - \eqref{2.2} and $u^n_h\in V_h$ for $n=1, 2, \dots, M$ be the solution for \eqref{2.3} - \eqref{2.4}. Then there holds the error estimate, see \cite{C87}
	\begin{align}\label{2.5}
		\left\|u_h-u\right\|_{L^2(Q)}=
		\begin{cases}
			O\left(h^2+\Delta t\right), &\theta=\{1\},\\
			O\left(h^2+\Delta t^2\right), &\theta=\{0.5\},
		\end{cases}		
	\end{align}
	where $h$ is the mesh size.
\end{dl}


% --------------------------------------------------------------------
\section{Tests and discussion}
%In this section, we investigate some numerical test to evaluate the accuracy and ability of the method. The important questions is how 
% software such as Ansys, Solidwork,... provide simulation features of heat transfer, but they lack of mathematical clarity for mathematicians.
% --------------------------------------------------------------------
\input{result}
\input{optimal_control_problem}


% --------------------------------------------------------------------
\section{Conclusion and perspective}
In this contribution, the heat equation is investigated with implicit time scheme and polynomial degree continuous Galerkin finite element method. From the numerical results, we establish that our method present a nice mesh convergence. So, it allows for reliable simulation during the heat transfer process and exhibits application of in thermal engineering. The solver can be extended to deal with other simulation of heat transfer or mechanical models. For this reason, the source code are available online at \url{https://github.com/hdnhan/seatuc2019/tree/master/freefem\%2B\%2B}. 
\\
It is noteworthy that the numerical results of present work is an important feature for our future research when we consider the heat problem in the context of optimal control problem \cite{HTLI14} or shape optimization, e.g \cite{TLP18}. 
% --------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{references}{}
\vfill

\end{document}
